\LARGE \bf Mean Estimation from One-Bit Measurements

### 2022-05-04 proof-lan-distributed.tex
arranged appendix in two-columns

We begin with an argument on the smoothness properties of the densities,
which is important for our Taylor expansions to come.
\begin{lemma}
  \label{lemma:derivative-bounds}
  Let Assumption~\ref{assumption:detection-regions}\eqref{item:lipschitz-density} hold. Then for any $A = \cup_{i = 1}^k
  [a_i, b_i]$ and $h \in \R$,
  \begin{align}
    \left|P_{\theta + h}(A) - P_\theta(A) - \dPtheta(A) h \right| \leq 
    k \cdot \lip(f) h^2,
    \label{eqn:expansion-dPtheta}
  \end{align}
  where
  \begin{align*}
    \dPtheta(A) = \sum_{i = 1}^k f(a_i - \theta) - f(b_i - \theta).
  \end{align*}
  Additionally, we have the bounds
  \begin{align}
    \label{eqn:bound-density-diffs}
    |f(b) - f(a)| \le 2 \sqrt{\lip(f) P([a, b])}
    ~~ \mbox{and} ~~
    |\dPtheta(A)| \le 2 \sqrt{k \lip(f)}.
  \end{align}
\end{lemma}
\noindent
See Section~\ref{sec:proof-derivative-bounds} for a proof.

The second lemma provides the local asymptotic normality we require.
\begin{lemma}
  \label{lemma:lan-bits}
  Let
  Assumption~\ref{assumption:detection-regions}\eqref{item:lipschitz-density}
  and~\eqref{item:finite-intervals} hold, and let $B_i = \indic{X_i \in
    A_i}$.  Let $h_n \to h \in \R$. Then for any $\theta \in
  \mbox{int}\Theta$,
  \begin{equation*}
    \sum_{i = 1}^n \log \frac{P_{\theta + h_n/\sqrt{n}}(B_i)}{
      P_\theta(B_i)}
    = \frac{h}{\sqrt{n}}
    \sum_{i = 1}^n \score_\theta(B_i)
    - \frac{h^2}{4n} \sum_{i = 1}^n \var(\score_\theta(B_i))
    - \frac{h^2}{4n} \sum_{i = 1}^n \score_\theta(B_i)^2
    + o_P(1).
  \end{equation*}
  If additionally
  Assumption~\ref{assumption:detection-regions}\eqref{item:limit-variance}
  holds, then
  \begin{equation*}
    \sum_{i = 1}^n \log \frac{P_{\theta + h_n/\sqrt{n}}(B_i)}{
      P_\theta(B_i)}
    = \frac{h}{\sqrt{n}}
    \sum_{i = 1}^n \score_\theta(B_i)
    - \frac{h^2}{2} \kappa(\theta) + o_P(1).
  \end{equation*}
\end{lemma}
\noindent
The proof of Lemma~\ref{lemma:lan-bits} is quite technical,
so we defer it to Section~\ref{sec:proof-lan-bits}.

@@

We now recall the familiar H\'{a}jek-Le-Cam local asymptotic minimax
result~\cite[Thm.~8.11]{VanDerVaart98}: if the family
$\{P_\theta\}$ is LAN with precision $\kappa(\theta)$, then
\begin{equation*}
  \liminf_{c \to \infty} \liminf_n \sup_{\norm{\tau - \theta} \le
    c / \sqrt{n}} \E_\tau\left[L(\sqrt{n}(\theta_n - \tau))\right]
  \ge \E[L(Z / \sqrt{\kappa(\theta)})]
\end{equation*}
for any symmetric quasi-convex loss $L$, where $Z \sim \normal(0, 1)$.
This immediately gives Theorem~\ref{theorem:non-adaptive-minimax}.

@@

To see the first claim of the lemma, we consider the simpler special case
that $A = [a, b]$. Then as $f$ is Lipschitz (and hence absolutely
continuous and a.e.\ differentiable with $\linf{f'} \le \lip(f)$),
we have
\begin{align*}
  P_{\theta + h}(A)
  - P_\theta(A)
  & = \int_a^b (f(z - \theta - h) - f(z - \theta)) dz \\
  & = -\int_a^b \int_0^h f'(z - \theta - u) du dz \\
  & = -\int_0^h \int_a^b f'(z - \theta - u) dz du \\
  & = \int_0^h f(a - \theta - u) - f(b - \theta - u) du \\
  & \lesseqgtr \int_0^h (f(a - \theta) - f(b - \theta)) du
  \pm 2 \int_0^h \lip(f) u du \\
  & = \left[f(a - \theta) - f(b - \theta)\right] h \pm \lip(f) h^2.
\end{align*}
This gives the first two claims of the lemma.

For the second, we require a bit more work.
Let $L = \lip(f)$ for shorthand. Let $a < b$.
Then we always have
\begin{equation}
  \label{eqn:interval-length-thing}
  P([a, b])
  \ge \int_a^b f(z) dz
  \ge \int_a^b \max\{f(b) - L (b - z), f(a) - L(z - a), 0\} dz.
\end{equation}
If $f(a) + f(b) \ge L (b - a)$, then the point $\hat{z} =
\frac{a + b}{2} - \frac{f(b) - f(a)}{2L}$ satisfies both $f(b) - L(b -
\hat{z}) \ge 0$ and $f(a) - L(\hat{z} - a) \ge 0$. The
integral~\eqref{eqn:interval-length-thing} then becomes
\begin{align*}
  \lefteqn{\int_a^{\hat{z}}
    (f(a) - L (z - a) dz)
    + \int_{\hat{z}}^b
    (f(b) - L (b - z)) dz} \\
  & = \frac{f(a) + f(b)}{2}
  \left(\frac{b - a}{2}\right)
  - L \left(\frac{b - a}{2} \right)^2
  + \frac{(f(b) - f(a))^2}{4L},
\end{align*}
and using the assumption that $\frac{f(a) + f(b)}{2} \ge L(b - a)$,
we obtain
\begin{align*}
  \frac{(f(b) - f(a))^2}{4L}
  & \le \frac{f(b) + f(b)}{2} \frac{b - a}{2}
  - L \left(\frac{b - a}{2}\right)^2
  + \frac{(f(b) - f(a))^2}{4L}
  \le P([a, b]).
\end{align*}
That is, $|f(b) - f(a)| \le 2 \sqrt{\lip(f) P([a, b])}$.
In the converse case that $f(a) + f(b) \le L(b - a)$, then
the integral~\eqref{eqn:interval-length-thing} becomes
\begin{align*}
  P([a, b])
  & \ge \int_a^{a + \frac{f(a)}{L}}
  (f(a) - L (z - a)) dz
  + \int_{b - \frac{f(b)}{L}}^b (f(b) - L (b - z)) dz \\
  & = \frac{f(a)^2}{L}
  - \frac{f(a)^2}{2L}
  + \frac{f(b)^2}{L}
  - \frac{f(b)^2}{2L},
\end{align*}
so that 
\begin{align*}
\newtext{\frac{f(a) + f(b)}{\sqrt{2}} \le} \sqrt{f(a)^2 + f(b)^2} \le \sqrt{2 \lip(f) P([a, b])},
\end{align*}
\newtext{where the left inequality follows from concavity of $\sqrt{\cdot}$.} In sum, we have demonstrated that always the first
bound~\eqref{eqn:bound-density-diffs} holds.
To show the second inequality in expression~\eqref{eqn:bound-density-diffs},
note that
$\sum_i P([a_i, b_i]) \le 1$, and apply Cauchy-Schwarz.

@@

Our proof follows that of \cite[Thm.~7.2]{VanDerVaart98} closely. We first
demonstrate a type of uniform quadratic mean differentiability
(Definition~\ref{definition:qmd}) for sets $A$ that are finite unions of
intervals. By a Taylor approximation and concavity of
$\sqrt{\cdot}$, we have
\begin{equation*}
  \sqrt{a} + \frac{b}{2 \sqrt{a}} -
  \frac{b^2}{4a^{\newtext{3/2}}}
  \le \sqrt{a + b} \le \sqrt{a}
  + \frac{b}{2 \sqrt{a}}
\end{equation*}
for any $a > 0$ and $|b| \le 3a/4$. Consequently,
recalling that $\score_\theta(A) = \dPtheta(A) / P_\theta(A)$,
for any $h \in \R$ and $A = \cup_{i = 1}^k [t_i^-, t_i^+]$ the
union of $k$ intervals, the expansion~\eqref{eqn:expansion-dPtheta} yields
\begin{equation*}
  \left(\sqrt{P_{\theta + h}(A)} -
  \sqrt{P_\theta(A)} - \half h \score_\theta(A) \sqrt{P_\theta(A)}
  \right)^2
  \le
  \left(
  \frac{k \lip(f)}{2 \sqrt{P_\theta(A)}} h^2
  + \frac{(|\dPtheta(A) h| + h^2 \lip(f))^2}{P_\theta(A)^{3/2}}
  \right)^2,
\end{equation*}
valid for $h$ such that
$|\dPtheta(A) h| \le P_\theta(A) / 4$ and
$k h^2 \lip^2(f) \le P_\theta(A) / 4$.
Thus, under
Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals},
there exists a numerical constant $C < \infty$ such that
\begin{subequations}
  \label{eqn:h-fourth}
  \begin{align}
    \nonumber \left(\sqrt{P_{\theta + h}(A)} -
    \sqrt{P_\theta(A)} - \half
    h \score_\theta(A) \sqrt{P_\theta(A)}\right)^2
    & \le
    \left(\frac{h^2 k \cdot \lip(f)}{2 \sqrt{P_\theta(A)}}
    + \frac{(|\dPtheta(A) h| + k h^2 \lip(f))^2}{
      P_\theta(A)^{3/2}}\right)^2 \\
    & \le \frac{C}{P_\theta(A)} \left[k^2 \lip^2(f)
      + \score_\theta(A)^2
      + \frac{k^4 h^4 \lip^4(f)}{P_\theta(A)^2}
      \right] \cdot h^4,
  \end{align}
  valid whenever $|\dPtheta(A) h|
  \le P_\theta(A) / 4$ and $k h^2 \lip^2(f) \le P_\theta(A) / 4$,
  and similarly, we have
  \begin{equation}
    \left(\sqrt{P_{\theta + h}(A^c)} -
    \sqrt{P_\theta(A^c)} - \half
    h \score_\theta(A^c) \sqrt{P_\theta(A^c)}\right)^2
    \le \frac{C}{P_\theta(A^c)}
    \left[k^2 \lip^2(f)
      + \score_\theta(A^c)^2
      + \frac{k^4 h^4 \lip^4(f)}{P_\theta(A^c)^2}
      \right] \cdot h^4.
  \end{equation}
\end{subequations}
That is, the family $\{P_\theta\}$ with bit observations $B_n$ satisfies a
uniform type of quadratic-mean differentiability
(Def.~\ref{definition:qmd}).

For shorthand, define $P_n = P_{\theta + h_n / \sqrt{n}}$ and $P =
P_\theta$, and let $p_n, p$ be shorthand for the p.m.f.s of the two
distributions.  For the sets $A_i$ we recall that $B_i = \indic{X_i \in
  A_i}$.  The random variables
\begin{equation*}
  W_{n,i} \defeq 2 \left(\sqrt{\frac{p_n}{p}}(B_i) - 1\right)
\end{equation*}
are with $P$-probability 1 well-defined, and by the
inequalities~\eqref{eqn:h-fourth}, we have
that
\begin{align}
  \lefteqn{\var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right)
    \le 
    C \frac{k_i^2 \lip^2(f) + \score_\theta(A_i)^2
      + \score_\theta(A_i^c)^2}{P_\theta(A_i) P_\theta(A_i^c)}
    \cdot \frac{h_n^4}{n^2}
    + C \frac{k^4 \lip^4(f)}{
      P_\theta(A_i)^3 P_\theta(A_i^c)^3}
    \frac{h_n^8}{n^4}} \nonumber \\
  & \qquad\qquad\qquad\qquad\qquad \le 
  C \frac{k_i^2 \lip^2(f) + \score_\theta(A_i)^2
  + \score_\theta(A_i^c)^2}{P_\theta(A_i) P_\theta(A_i^c)}
  \cdot \frac{h_n^4}{n^2}
  + C \frac{k^4 \lip^4(f)}{
    P_\theta(A_i)^3 P_\theta(A_i^c)^3}
  \frac{h_n^8}{n^4}
  \label{eqn:var-wni-expansion}
\end{align}
whenever
\begin{equation*}
  \frac{h}{\sqrt{n}} \max\{\score_\theta(A_i),
  \score_\theta(A_i^c)\}
  \le \frac{1}{4}
  ~~ \mbox{and} ~~
  \frac{k_i h_n^2}{n} \lip^2(f)
  \le \frac{\min\{P_\theta(A_i), P_\theta(A_i^c)\}}{4}
\end{equation*}
Now, we use
Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals},
coupled with Lemma~\ref{lemma:derivative-bounds} to show that the summed
variances converge to zero.  Indeed, Lemma~\ref{lemma:derivative-bounds} and
inequality~\eqref{eqn:var-wni-expansion} give that
\begin{equation*}
  \var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right)
  \le C \cdot
  \left[\frac{k_i^2}{P_\theta(A_i) P_\theta(A_i^c)}
    \frac{1}{n}
    + \frac{k_i}{P_\theta(A_i) P_\theta(A_i^c)}
    \frac{1}{n}
    + \frac{k_i^4}{P_\theta(A_i)^3 P_\theta(A_i^c)^3}
    \frac{1}{n^3}\right] \frac{1}{n},
\end{equation*}
where $C < \infty$ depends only on $\lip(f)$ and $h_n$ (both of which are
uniformly bounded) whenever
\begin{equation*}
  \frac{k_i}{P_\theta(A_i) P_\theta(A_i^c)} \frac{1}{n} \le
  \frac{1}{C}.
\end{equation*}
Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals}
thus implies that $\E[\score_\theta(B_i)] = 0$ and
\begin{equation}
  \label{eqn:summed-variances-to-zero}
  \var\left(\sum_{i = 1}^n W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)
  \right)
  = \sum_{i = 1}^n \var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)
  \right)
  \to 0.
\end{equation}

We now control the expectation of the $W_{n,i}$. Defining $\mu_i$ to be the
induced counting measure on $B_i = \indic{X_i \in A_i}$,
\begin{align*}
  \sum_{i = 1}^n \E[W_{n,i}]
  & = 2\sum_{i = 1}^n
  \left(\int \sqrt{p_n(b)} \sqrt{p(b)} d\mu_i(b) - 1 \right)
  = -\sum_{i = 1}^n \int \left(\sqrt{p_n(b)} - \sqrt{p(b)}\right)^2
  d\mu_i(b) \\
  & = -\frac{h_n^2}{4 n} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]
  - \sum_{i = 1}^n \int \left(\sqrt{p_n(b)} - \sqrt{p(b)}
  - \frac{h_n}{\sqrt{n}} \score_\theta(b) \sqrt{p(b)}\right)^2 d\mu_i(b) \\
  & \qquad \qquad ~
  - \sum_{i = 1}^n \int \left(\sqrt{p_n(b)} - \sqrt{p(b)}
  - \frac{h_n}{\sqrt{n}} \score_\theta(b) \sqrt{p(b)}\right)
  \frac{h_n}{\sqrt{n}} \score_\theta(b) \sqrt{p(b)}d\mu_i(b) \\
  & = -\bigg(\frac{h^2}{4n} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]\bigg)
  - o(1)
\end{align*}
uniformly in $h$, with a derivation completely paralleling that above.
Therefore, we obtain
\begin{equation*}
  \sum_{i = 1}^n W_{n,i}
  = \sum_{i = 1}^n \left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right)
  + \frac{h_n}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
  = -\frac{h^2}{4n} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]
  + \frac{h}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
  + o_P(1),
\end{equation*}
where we have used that $h_n \to h$.

>>>>

We begin with an argument on the smoothness properties of the densities,
which is important for our Taylor expansions to come.
\begin{lemma}
  \label{lemma:derivative-bounds}
  Let Assumption~\ref{assumption:detection-regions}\eqref{item:lipschitz-density} hold. Then for any $A = \cup_{i = 1}^k
  [a_i, b_i]$ and $h \in \R$,
  \begin{align}
    \left|P_{\theta + h}(A) - P_\theta(A) - \dPtheta(A) h \right| \leq 
    k \cdot \lip(f) h^2,
    \label{eqn:expansion-dPtheta}
  \end{align}
  where
  \begin{align*}
    \dPtheta(A) = \sum_{i = 1}^k f(a_i - \theta) - f(b_i - \theta).
  \end{align*}
  Additionally, we have the bounds
  \begin{align}
    & \label{eqn:bound-density-diffs}
    |f(b) - f(a)| \le 2 \sqrt{\lip(f) P([a, b])} \\
    & 
    ~~ \mbox{and} ~~
    |\dPtheta(A)| \le 2 \sqrt{k \lip(f)}. \nonumber
  \end{align}
\end{lemma}
\noindent
See Section~\ref{sec:proof-derivative-bounds} for a proof.

The second lemma provides the local asymptotic normality we require.
\begin{lemma}
  \label{lemma:lan-bits}
  Let
  Assumption~\ref{assumption:detection-regions}\eqref{item:lipschitz-density}
  and~\eqref{item:finite-intervals} hold, and let $B_i = \indic{X_i \in
    A_i}$.  Let $h_n \to h \in \R$. Then for any $\theta \in
  \mbox{int}\Theta$,
  \begin{align*}
    & \sum_{i = 1}^n \log \frac{P_{\theta + h_n/\sqrt{n}}(B_i)}{
      P_\theta(B_i)} \\
    & \qquad = \frac{h}{\sqrt{n}}
    \sum_{i = 1}^n \score_\theta(B_i) - \frac{h^2}{4n} \sum_{i = 1}^n \var(\score_\theta(B_i)) \\
    & \qquad \qquad - \frac{h^2}{4n} \sum_{i = 1}^n \score_\theta(B_i)^2
    + o_P(1).
  \end{align*}
  If additionally
  Assumption~\ref{assumption:detection-regions}\eqref{item:limit-variance}
  holds, then
  \begin{equation*}
    \sum_{i = 1}^n \log \frac{P_{\theta + h_n/\sqrt{n}}(B_i)}{
      P_\theta(B_i)}
    = \frac{h}{\sqrt{n}}
    \sum_{i = 1}^n \score_\theta(B_i)
    - \frac{h^2}{2} \kappa(\theta) + o_P(1).
  \end{equation*}
\end{lemma}
\noindent
The proof of Lemma~\ref{lemma:lan-bits} is quite technical,
so we defer it to Section~\ref{sec:proof-lan-bits}.

@@

We now recall the familiar H\'{a}jek-Le-Cam local asymptotic minimax
result~\cite[Thm.~8.11]{VanDerVaart98}: if the family
$\{P_\theta\}$ is LAN with precision $\kappa(\theta)$, then
\begin{align*}
  \liminf_{c \to \infty} & \liminf_n \sup_{\norm{\tau - \theta} \le
    c / \sqrt{n}} \E_\tau\left[L(\sqrt{n}(\theta_n - \tau))\right] \\
  & \qquad  \ge \E[L(Z / \sqrt{\kappa(\theta)})]
\end{align*}
for any symmetric quasi-convex loss $L$, where $Z \sim \normal(0, 1)$.
This immediately gives Theorem~\ref{theorem:non-adaptive-minimax}.

@@

To see the first claim of the lemma, we consider the simpler special case
that $A = [a, b]$. Then as $f$ is Lipschitz (and hence absolutely
continuous and a.e.\ differentiable with $\linf{f'} \le \lip(f)$),
we have
\begin{align*}
  & P_{\theta + h}(A)
  - P_\theta(A)
   = \int_a^b (f(z - \theta - h) - f(z - \theta)) dz \\
  & \qquad = -\int_a^b \int_0^h f'(z - \theta - u) du dz \\
  & \qquad = -\int_0^h \int_a^b f'(z - \theta - u) dz du \\
  & \qquad = \int_0^h f(a - \theta - u) - f(b - \theta - u) du \\
  & \qquad \lesseqgtr \int_0^h (f(a - \theta) - f(b - \theta)) du
  \pm 2 \int_0^h \lip(f) u du \\
  & \qquad = \left[f(a - \theta) - f(b - \theta)\right] h \pm \lip(f) h^2.
\end{align*}
This gives the first two claims of the lemma.

For the second, we require a bit more work.
Let $L = \lip(f)$ for shorthand. Let $a < b$.
Then we always have
\begin{align}
  \label{eqn:interval-length-thing}
  & P([a, b]) \ge \int_a^b f(z) dz \\
  & \quad \ge \int_a^b \max\{f(b) - L (b - z), f(a) - L(z - a), 0\} dz. \nonumber
\end{align}
If $f(a) + f(b) \ge L (b - a)$, then the point $\hat{z} =
\frac{a + b}{2} - \frac{f(b) - f(a)}{2L}$ satisfies both $f(b) - L(b -
\hat{z}) \ge 0$ and $f(a) - L(\hat{z} - a) \ge 0$. The
integral~\eqref{eqn:interval-length-thing} then becomes
\begin{align*}
  \lefteqn{\int_a^{\hat{z}}
    (f(a) - L (z - a) dz)
    + \int_{\hat{z}}^b
    (f(b) - L (b - z)) dz} \\
  & = \medmath{\frac{f(a) + f(b)}{2}
  \left(\frac{b - a}{2}\right)
  - L \left(\frac{b - a}{2} \right)^2
  + \frac{(f(b) - f(a))^2}{4L}},
\end{align*}
and using the assumption that $\frac{f(a) + f(b)}{2} \ge L(b - a)$,
we obtain
\begin{align*}
  \frac{(f(b) - f(a))^2}{4L}
  & \le \frac{f(b) + f(b)}{2} \frac{b - a}{2} \\
  & \qquad - L \left(\frac{b - a}{2}\right)^2
  + \frac{(f(b) - f(a))^2}{4L} \\
  & \le P([a, b]).
\end{align*}
That is, $|f(b) - f(a)| \le 2 \sqrt{\lip(f) P([a, b])}$.
In the converse case that $f(a) + f(b) \le L(b - a)$, then
the integral~\eqref{eqn:interval-length-thing} becomes
\begin{align*}
  P([a, b])
  & \ge \int_a^{a + \frac{f(a)}{L}}
  (f(a) - L (z - a)) dz \\
  & \qquad + \int_{b - \frac{f(b)}{L}}^b (f(b) - L (b - z)) dz \\
  & = \frac{f(a)^2}{L}
  - \frac{f(a)^2}{2L}
  + \frac{f(b)^2}{L}
  - \frac{f(b)^2}{2L},
\end{align*}
so that 
\begin{align*}
\newtext{\frac{f(a) + f(b)}{\sqrt{2}} \le} \sqrt{f(a)^2 + f(b)^2} \le \sqrt{2 \lip(f) P([a, b])},
\end{align*}
\newtext{where the left inequality follows from concavity of $\sqrt{\cdot}$.} In sum, we have demonstrated that always the first
bound~\eqref{eqn:bound-density-diffs} holds.
To show the second inequality in expression~\eqref{eqn:bound-density-diffs},
note that
$\sum_i P([a_i, b_i]) \le 1$, and apply Cauchy-Schwarz.

@@

Our proof follows that of \cite[Thm.~7.2]{VanDerVaart98} closely. We first
demonstrate a type of uniform quadratic mean differentiability
(Definition~\ref{definition:qmd}) for sets $A$ that are finite unions of
intervals. By a Taylor approximation and concavity of
$\sqrt{\cdot}$, we have
\begin{equation*}
  \sqrt{a} + \frac{b}{2 \sqrt{a}} -
  \frac{b^2}{4a^{\newtext{3/2}}}
  \le \sqrt{a + b} \le \sqrt{a}
  + \frac{b}{2 \sqrt{a}}
\end{equation*}
for any $a > 0$ and $|b| \le 3a/4$. Consequently,
recalling that $\score_\theta(A) = \dPtheta(A) / P_\theta(A)$,
for any $h \in \R$ and $A = \cup_{i = 1}^k [t_i^-, t_i^+]$ the
union of $k$ intervals, the expansion~\eqref{eqn:expansion-dPtheta} yields
\begin{align*}
  & \left(\sqrt{P_{\theta + h}(A)} -
  \sqrt{P_\theta(A)} - \half h \score_\theta(A) \sqrt{P_\theta(A)}
  \right)^2 \\
  & \quad \le
  \left(
  \frac{k \lip(f)}{2 \sqrt{P_\theta(A)}} h^2
  + \frac{(|\dPtheta(A) h| + h^2 \lip(f))^2}{P_\theta(A)^{3/2}}
  \right)^2,
\end{align*}
valid for $h$ such that
$|\dPtheta(A) h| \le P_\theta(A) / 4$ and
$k h^2 \lip^2(f) \le P_\theta(A) / 4$.
Thus, under
Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals},
there exists a numerical constant $C < \infty$ such that
\begin{subequations}
  \label{eqn:h-fourth}
  \begin{align}
    & \nonumber \left(\sqrt{P_{\theta + h}(A)} -
    \sqrt{P_\theta(A)} - \half
    h \score_\theta(A) \sqrt{P_\theta(A)}\right)^2 \\
    & \nonumber \quad \le
    \left(\frac{h^2 k \cdot \lip(f)}{2 \sqrt{P_\theta(A)}}
    + \frac{(|\dPtheta(A) h| + k h^2 \lip(f))^2}{
      P_\theta(A)^{3/2}}\right)^2 \\
    & \quad \le \frac{C}{P_\theta(A)} \left[k^2 \lip^2(f)
      + \score_\theta(A)^2
      + \frac{k^4 h^4 \lip^4(f)}{P_\theta(A)^2}
      \right] \cdot h^4,
  \end{align}
  valid whenever $|\dPtheta(A) h|
  \le P_\theta(A) / 4$ and $k h^2 \lip^2(f) \le P_\theta(A) / 4$,
  and similarly, we have
  \begin{align}
    & \left(\sqrt{P_{\theta + h}(A^c)} -
    \sqrt{P_\theta(A^c)} - \half
    h \score_\theta(A^c) \sqrt{P_\theta(A^c)}\right)^2 \nonumber \\
    & ~~ \le \frac{C}{P_\theta(A^c)}
    \left[k^2 \lip^2(f)
      + \score_\theta(A^c)^2
      + \frac{k^4 h^4 \lip^4(f)}{P_\theta(A^c)^2}
      \right] \cdot h^4. 
  \end{align}
\end{subequations}
That is, the family $\{P_\theta\}$ with bit observations $B_n$ satisfies a
uniform type of quadratic-mean differentiability
(Def.~\ref{definition:qmd}).

For shorthand, define $P_n = P_{\theta + h_n / \sqrt{n}}$ and $P =
P_\theta$, and let $p_n, p$ be shorthand for the p.m.f.s of the two
distributions.  For the sets $A_i$ we recall that $B_i = \indic{X_i \in
  A_i}$.  The random variables
\begin{equation*}
  W_{n,i} \defeq 2 \left(\sqrt{\frac{p_n}{p}}(B_i) - 1\right)
\end{equation*}
are with $P$-probability 1 well-defined, and by the
inequalities~\eqref{eqn:h-fourth}, we have
that
\begin{align}
\label{eqn:var-wni-expansion}
  & \var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right) \\
    & \quad \le C \frac{k_i^2 \lip^2(f) + \score_\theta(A_i)^2
      + \score_\theta(A_i^c)^2}{P_\theta(A_i) P_\theta(A_i^c)}
    \cdot \frac{h_n^4}{n^2} \nonumber \\
    & \qquad + C \frac{k^4 \lip^4(f)}{
      P_\theta(A_i)^3 P_\theta(A_i^c)^3}
    \frac{h_n^8}{n^4} \nonumber \\
  & \quad \le 
  C \frac{k_i^2 \lip^2(f) + \score_\theta(A_i)^2
  + \score_\theta(A_i^c)^2}{P_\theta(A_i) P_\theta(A_i^c)}
  \cdot \frac{h_n^4}{n^2} \\
  & \qquad + C \frac{k^4 \lip^4(f)}{
    P_\theta(A_i)^3 P_\theta(A_i^c)^3}
  \frac{h_n^8}{n^4}
\end{align}
whenever
\begin{align*}
  & \frac{h}{\sqrt{n}} \max\{\score_\theta(A_i),
  \score_\theta(A_i^c)\}
  \le \frac{1}{4} \\
  & ~~ \mbox{and} ~~
  \frac{k_i h_n^2}{n} \lip^2(f)
  \le \frac{\min\{P_\theta(A_i), P_\theta(A_i^c)\}}{4}
\end{align*}
Now, we use
Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals},
coupled with Lemma~\ref{lemma:derivative-bounds} to show that the summed
variances converge to zero.  Indeed, Lemma~\ref{lemma:derivative-bounds} and
inequality~\eqref{eqn:var-wni-expansion} give that
\begin{align*}
  & \var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right)
   \le C \cdot
  \left[\frac{k_i^2}{P_\theta(A_i) P_\theta(A_i^c)}
    \frac{1}{n} \right. \\
    & \left. \qquad + \frac{k_i}{P_\theta(A_i) P_\theta(A_i^c)}
    \frac{1}{n}
    + \frac{k_i^4}{P_\theta(A_i)^3 P_\theta(A_i^c)^3}
    \frac{1}{n^3}\right] \frac{1}{n},
\end{align*}
where $C < \infty$ depends only on $\lip(f)$ and $h_n$ (both of which are
uniformly bounded) whenever
\begin{equation*}
  \frac{k_i}{P_\theta(A_i) P_\theta(A_i^c)} \frac{1}{n} \le
  \frac{1}{C}.
\end{equation*}
Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals}
thus implies that $\E[\score_\theta(B_i)] = 0$ and
\begin{align}
  & \var\left(\sum_{i = 1}^n W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)
  \right) \nonumber \\
  & \qquad = \sum_{i = 1}^n \var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)
  \right)
  \to 0. \label{eqn:summed-variances-to-zero}
\end{align}

We now control the expectation of the $W_{n,i}$. Defining $\mu_i$ to be the
induced counting measure on $B_i = \indic{X_i \in A_i}$,
\begin{align*}
  & \sum_{i = 1}^n \E[W_{n,i}]
  = 2\sum_{i = 1}^n
  \left(\int \sqrt{p_n(b)} \sqrt{p(b)} d\mu_i(b) - 1 \right) \\
  & \quad = -\sum_{i = 1}^n \int \left(\sqrt{p_n(b)} - \sqrt{p(b)}\right)^2
  d\mu_i(b) \\
  & \quad = -\frac{h_n^2}{4 n} \sum_{i = 1}^n \E[\score_\theta(B_i)^2] \\
  & \qquad 
  - \sum_{i = 1}^n \int \left(\sqrt{p_n(b)} - \sqrt{p(b)}
  - \frac{h_n}{\sqrt{n}} \score_\theta(b) \sqrt{p(b)}\right)^2 d\mu_i(b) \\
  & \qquad \medmath{
  - \sum_{i = 1}^n \int \left(\sqrt{p_n(b)} - \sqrt{p(b)}
  - \frac{h_n}{\sqrt{n}} \score_\theta(b) \sqrt{p(b)}\right)
  \frac{h_n}{\sqrt{n}} \score_\theta(b) \sqrt{p(b)}d\mu_i(b)} \\
  & = -\bigg(\frac{h^2}{4n} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]\bigg)
  - o(1)
\end{align*}
uniformly in $h$, with a derivation completely paralleling that above.
Therefore, we obtain
\begin{align*}
   \sum_{i = 1}^n W_{n,i} & = \sum_{i = 1}^n \left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right)
  + \frac{h_n}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i) \\
  & = -\frac{h^2}{4n} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]
  + \frac{h}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
  + o_P(1),
\end{align*}
where we have used that $h_n \to h$.

Now, we write the log-likelihood ratio. We have
\begin{align*}
  & \sum_{i = 1}^n \log \frac{p_n(B_i)}{p(B_i)}
  = 2 \sum_{i = 1}^n \log\left(1 + \half W_{n,i}\right) \\
  & \qquad  = \sum_{i = 1}^n W_{n,i}
  - \frac{1}{4} \sum_{i = 1}^n W_{n,i}^2
  + \half \sum_{i = 1}^n W_{n,i}^2 R(W_{n,i})
\end{align*}
where the remainder $|R(W_{n,i})| \le |W_{n,i}|$ for $|W_{n,i}| \le 1$.
Using the Taylor expansions of $\sqrt{\cdot}$ and
Lemma~\ref{lemma:derivative-bounds}, we have
\begin{align}
  &\left| \half W_{n,i} \right|
   \leq \half \left| \score_\theta(B_i) \right|
  \frac{h_n}{\sqrt{n}} \nonumber \\
  & \qquad + \left|\frac{h_n^2}{n} \frac{k_i \lip(f)}{p(B_i)}
  + \frac{h_n^2}{n} \score_\theta(B_i)^2
  + \frac{ h_n^4}{n^2} \frac{k_i^2 \lip(f)^2}{p(B_i)^2}\right| \nonumber \\
  & \quad = \half \score_\theta(B_i)
  \frac{h_n}{\sqrt{n}} \nonumber \\
  & \qquad + 
  C \left|\frac{\sqrt{k_i}}{\sqrt{n} p(B_i)}
  + \frac{k_i}{n p(B_i)}
  + \frac{\sqrt{k_i}}{p(B_i)^2 n}
  + \frac{k_i^2}{p(B_i)^2 n^2}
  \right|
  \label{eqn:max-wni-zero}
\end{align}
where $|C| < \infty$ depends only on $\lip(f)$ and $h_n$ and so is
uniformly bounded. From Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals} we get
\[
C \left|\frac{\sqrt{k_i}}{\sqrt{n} p(B_i)}
  + \frac{k_i}{n p(B_i)}
  + \frac{\sqrt{k_i}}{p(B_i)^2 n}
  + \frac{k_i^2}{p(B_i)^2 n^2}
  \right| \to 0. 
\]
Consequently $\max_i W_{n,i} \to 0$, so that
\begin{align}
  \label{eqn:almost-at-the-end}
  \sum_{i = 1}^n \log \frac{p_n(B_i)}{p(B_i)}
  & = \frac{h_n}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
  - \frac{1}{4} \sum_{i = 1}^n \E[\score_\theta(B_i)^2] \\
  & \qquad - \frac{1}{4} \sum_{i = 1}^n W_{n,i}^2 + o_P(1). \nonumber
\end{align}
